### 2016-08-29 mcmc.tex
autocorrelation function calculation

\begin{problem}\label{prob:estimatetau}
Write a piece of code that computes the empirical autocorrelation
function.
You can speed this computation up considerably by using a fast Fourier
transform.
Run this on the chain you obtained from \problemname~\ref{prob:MH}.
Plot the autocorrelation function you find at short lags ($\Delta < 100$).
This plot should resemble \figurename~\ref{fig:estimatetau}.
\end{problem}

>>>>

\begin{problem}\label{prob:estimatetau}
Write a piece of code that computes the empirical autocorrelation
function.
You will probably want to speed this computation up by using a fast Fourier
transform\note{%
The calculation of the autocorrelation function can be seen as a convolution
and it can, therefore, be computed using the fast Fourier transform in
$\mathcal{O}(N\,\log N)$ operations instead of $\mathcal{O}(N^2)$ for a naive
implementation.}.
Run this on the chain you obtained from \problemname~\ref{prob:MH}.
Plot the autocorrelation function you find at short lags ($\Delta < 100$).
This plot should resemble \figurename~\ref{fig:estimatetau}.
\end{problem}
